CF Nutrition Pre- and Post-CFTR Modulator

### 2022-09-23 Edith Zemanick/CF Nutrition/cf_nutrition.qmd
added LFTs

```{r include=FALSE}
library(readxl)
library(tidyverse)
library(arsenal)
```

```{r}
#

```

@@

-   All values prior to effective modulator start were averaged to calculate the "pre" value. We selected the most recent vitamin values as the "post" value, and included any BMI percentile and FEV1 % predicted measures within a month of that visit.

@@

# Grouped by First Modulator

@@

```{r results='asis'}
p = paired(Timepoint~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile,data = df,id=ID,control = list(numeric.test = "signed.rank"))
summary(p,pfootnote = T)
```

>>>>

```{r include=FALSE}
library(readxl)
library(tidyverse)
library(parsedate)
library(arsenal)
```

```{r}
# Import all data
df = read.csv("/Users/timvigers/Documents/Work/Vigers/CF/Edith Zemanick/CF Nutrition/Data_Cleaned/analysis.csv")
df$Timepoint = factor(df$Timepoint,levels = c("Pre","Post"))
```

@@

-   All values prior to effective modulator start were averaged to calculate the "pre" value. We selected the most recent vitamin values as the "post" value, and included any BMI percentile, FEV1 % predicted, ALT, AST, and GGTP measures within a month of that visit.

@@

# Baseline value grouped by first modulator

```{r}
t1 = tableby(First.Modulator~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile+ALT+AST+GGTP,data = df[df$Timepoint == "Pre",])
summary(t1,pfootnote = T)
```

@@

```{r results='asis'}
p = paired(Timepoint~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile+ALT+AST+GGTP,data = df,id=ID,control = list(numeric.test = "signed.rank"))
summary(p,pfootnote = T)
```
